### 2021-05-11 doc/thesis/chapters/dsp.tex
diagram

\includepicture [0.7] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}.} {bd_freq_discriminator} {img/bd_freq_discriminator}

>>>>

\includepicture [0.75] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}.} {bd_freq_discriminator} {img/draw.io/bd_freq_discriminator}
